---
title: "README"
author: "Zoe Meers"
date: "30/06/2018"
output: 
  html_document:
    keep_md: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
source("R/parliament_data.R")
source("R/helper_funcs.R")
#source("R/geom_majorityline.R")
election_data <- readRDS(file="data/election_data.rda")
library(tidyverse)
```

# Parliament plots

This package attempts to implement "parliament plots" - visual representations of the composition of legislatures that display seats color-coded by party. The input is a data frame containing one row per party, with columns representing party name/label and number of seats, respectively.

This `R` package is a `ggplot2` extension.

To install the package:
```{r, eval=FALSE}
devtools::install_github("robwhickman/ggparliament")
```

Inspiration from this package comes from: [parliamentdiagram](https://github.com/slashme/parliamentdiagram), which
is used on Wikipedia, [parliament-svg](https://github.com/juliuste/parliament-svg), which is a
javascript clone, and [a discussion on StackOverflow](http://stackoverflow.com/questions/42729174/creating-a-half-donut-or-parliamentary-seating-chart), which provided some of the code for part for the "arc" representations used in this package.

Unique parliament layouts:
==========================

[This is a *Washington Post* article on parliament layouts.](https://www.washingtonpost.com/news/monkey-cage/wp/2017/03/04/these-5-designs-influence-every-legislature-in-the-world-and-tell-you-how-each-governs/?utm_term=.e1e1c1c3c37b)
It is a pretty useful reference.


## Semicircle parliament

### EU, France, United States, and so on...


### Plot of US Congress


```{r}
us_congress <- election_data %>%
  filter(country == "USA" &
    year == "2016" &
    house == "Representatives")

us_congress1 <- parliament_data(election_data = us_congress,
  type = "semicircle",
  total_seats = sum(us_congress$seats),
  parl_rows = 10,
  party_names = us_congress$party_short,
  party_seats = us_congress$seats)

us_senate <- election_data %>%
  filter(country == "USA" &
    year == "2016" &
    house == "Senate")


us_senate <- parliament_data(
  election_data = us_senate,
  type = "semicircle",
  total_seats = sum(us_senate$seats),
  parl_rows = 4,
  party_names = us_senate$party_short,
  party_seats = us_senate$seats)

```

```{r}
ggplot(us_congress1, aes(x, y, colour = party_short)) +
  geom_parliament_seats() + 
  geom_highlight_government(government == 1) +
  theme_void() +
  labs(colour = "", title = "United States Congress") +
  annotate("text", x=0, y=0, label=paste("Total:", sum(us_congress$seats), "Reps"), fontface="bold", size=8) +
  scale_colour_manual(values = us_congress1$colour, 
                      limits = us_congress1$party_short)
```

### Plot of US Senate

```{r}
senate <- ggplot(us_senate, aes(x=x, y=y, colour=party_long)) +
  geom_parliament_seats() + 
  geom_highlight_government(government == 1) +
  theme_void() +
  labs(colour = "", 
       title = "United States Senate",
       subtitle = "The party that has control of the Senate is encircled in black.") +
  scale_colour_manual(values = us_senate$colour, limits=us_senate$party_long)
senate 
```


### Plot of German Bundestag

```{r, fig.height=6, fig.width=10}
germany <- election_data %>%
  filter(year==2017 & country=="Germany") 

germany <- parliament_data(election_data=germany, 
                           total_seats = sum(germany$seats), 
                           parl_rows=10,
                           party_seats=germany$seats, 
                           type='semicircle')

ggplot(germany, aes(x,y,colour=party_short))+
  geom_parliament_seats()+
  geom_highlight_government(government==1) + 
  labs(colour="Party", title="Germany 2017 Election Results") + 
  theme_void()+
  scale_colour_manual(values = germany$colour, limits=germany$party_short)
```

## Opposing Benches Parliament

### United Kingdom

```{r, fig.height=6}
#data preparation
uk_17 <- election_data %>% 
  filter(country=="UK" & year=="2017")


uk_17_left <- uk_17 %>% 
  filter(government==0)
uk_17_right <- uk_17 %>% 
  filter(government==1)


uk_17_left <- parliament_data(election_data = uk_17_left,
  total_seats = sum(uk_17_left$seats),
  party_seats =  uk_17_left$seats,
  parl_rows = 10,
  type = "opposing_benches")


uk_17_right <- parliament_data(election_data = uk_17_right,
  total_seats = sum(uk_17_right$seats),
  party_seats = uk_17_right$seats,
  parl_rows = 9,
  type = "opposing_benches")

right <- ggplot(uk_17_right, aes(x, y, color=party_short)) +
  geom_parliament_seats() + 
  theme_void() +
  labs(colour = "") +
  geom_highlight_government(government==1) + 
  scale_colour_manual(values = uk_17_right$colour, 
                      limits = uk_17_right$party_short) +
  theme(legend.position = 'right')


left <- ggplot(uk_17_left, aes(x, y, color=party_short)) +
  geom_parliament_seats() + 
  theme_void() +
  labs(colour = "", 
       title = "UK parliament in 2017",
       subtitle="Government encircled in black.") +
  scale_colour_manual(values = uk_17_left$colour, 
                      limits = uk_17_left$party_short) +
  theme(legend.position = 'left') 

uk_parliament<- combine_opposingbenches(left=left, right=right)
uk_parliament

```



## Horseshoe parliament

### Australia, New Zealand

```{r}
australia <- election_data %>%
  filter(country == "Australia" &
    house == "Representatives" &
    year == "2016") 

australia <- parliament_data(election_data = australia,
  total_seats = sum(australia$seats),
  party_seats = australia$seats,
  parl_rows = 4,
  type = "horseshoe")
```

### Plot of Australian parliament

```{r,fig.width=4, fig.height=4}
au <-ggplot(australia, aes(x, y, color=party_short)) +
  geom_parliament_seats() + 
  theme_void() +
  geom_highlight_government(government==1) + 
  labs(colour = "", 
       title = "Australian Parliament",
       subtitle = "Government encircled in black.") +
  scale_colour_manual(values = australia$colour, 
                      limits = australia$party_short) + 
  theme(legend.position = 'bottom') 
au
```



# Faceting the data
 

If you want to facet a parliament, you can use a split-apply-combine strategy in a `dplyr` chain.

## Steps
You must:

1) split by year
2) apply the coordinates for each party
3) combine the rows into one large data frame.

A few examples are as follows:

### American Congress from 2010 onwards
```{r}
usa <- election_data %>%
  filter(country == "USA" &
    house == "Representatives")  %>% 
  split(.$year) %>% # split
  map(~parliament_data(election_data = ., #apply
  total_seats = sum(.$seats),
  party_seats = .$seats,
  parl_rows = 8,
  type = "semicircle")) %>%
  bind_rows() # combine
```

```{r, fig.width=12, fig.height=4}
ggplot(usa, aes(x, y, color=party_short)) +
  geom_parliament_seats() + 
  theme_void() +
  geom_highlight_government(government==1) + 
  labs(colour = "", 
       title = "American Congress",
       subtitle = "The party that has control of US Congress is encircled in black.") +
  scale_colour_manual(values = usa$colour, 
                      limits = usa$party_short) + 
  theme(legend.position = 'bottom') + 
  facet_grid(~year, scales='free')
```


### Facet Australian Parliament by House
```{r}
australia <- election_data %>%
  filter(country == "Australia" &
    year == "2016")  %>% 
  split(.$house) %>% # split
  map(~parliament_data(election_data = ., # apply
  total_seats = sum(.$seats),
  party_seats = .$seats,
  parl_rows = 4,
  type = "horseshoe")) %>%
  bind_rows() # combine
```

```{r,fig.width=8, fig.height=5}
ggplot(australia, aes(x, y, color=party_short)) +
  geom_parliament_seats() + 
  theme_void() +
  geom_highlight_government(government==1) + 
  labs(colour = "", 
       title = "Australian Parliament",
       subtitle = "Government encircled in black.") +
  scale_colour_manual(values = australia$colour, 
                      limits = australia$party_short) + 
  theme(legend.position = 'bottom') + 
  facet_grid(~house, scales='free')

```

### Facet UK Parliament

```{r}
uk_left<- election_data %>%
  filter(country == "UK" & government==0)  %>%
  split(.$year) %>%
  map(~parliament_data(election_data = .,
  total_seats = sum(.$seats),
  party_seats = .$seats,
  parl_rows = 12,
  type = "opposing_benches")) %>%
  bind_rows()

uk_right<-election_data %>%
  filter(country == "UK" & government=="1")  %>%
  split(.$year) %>%
  map(~parliament_data(election_data = .,
  total_seats = sum(.$seats),
  party_seats = .$seats,
  parl_rows = 14,
  type = "opposing_benches")) %>%
  bind_rows()


```


```{r, fig.height=10}
right <- ggplot(uk_right, aes(x, y, color=party_short)) +
  geom_parliament_seats() + 
  theme_void() +
  labs(colour = "") +
  geom_highlight_government(government==1) + 
  scale_colour_manual(values = uk_right$colour, 
                      limits = uk_right$party_short) +
  theme(legend.position = 'right')+
  facet_wrap(~year, ncol=1)


left <- ggplot(uk_left, aes(x, y, color=party_short)) +
  geom_parliament_seats() + 
  theme_void() +
  labs(colour = "", 
       title = "UK parliament",
       subtitle="Government encircled in black.") +
  scale_colour_manual(values = uk_left$colour, 
                      limits = uk_left$party_short) +
  theme(legend.position = 'left') +
  facet_wrap(~year, ncol=1)

uk_parliament_10_15_17 <- combine_opposingbenches(left=left, right=right)
uk_parliament_10_15_17
```

# TODO

## Women in parliament

`geom_women_in_parliament()` now exists. When the user defines women MPs in the plot, the alpha on other MPs is set to 0.5, effectively bringing women to the forefront.

## Electoral quotas

`geom_electoral_quota()` has been created. It plots an X on top of the original point. I think we can think of more creative things to do here... I wonder if there are any data that show whether someone was elected through a quota or through the "regular" process.

**Note**: `geom_women_in_parliament()` and `geom_electoral_quota()` have not yet been incorporated into `parliament_data()`. I think the best way to do that is to include aggregate data on women as well as those elected through a quota process as two new variables, and then expand that number to a long logical variable. i.e. if the Australian Labor Party has 48 female MPs in the House of Representatives in 2016, that column will expand into 48 1s and 0 for the remainder.

## Majority line (experimental)

* Note: this significant needs work!

I am working on creating a geom for a majority line. Essentially, this is a wrapper for `geom_segment()`. I would love to create a new geom, where x is 0 and y and yend are the end points for the points.
  * This is 8 and 10 for the horseshoe style 
  * 1 and 2 for the semicircle style
I haven't figured it out but I'm not the best programmer so I'm sure it's completely obvious!


## Labels

* This also needs work
Happy to take a look at your previous code, Rob, and add back into this branch.


