---
title: "How to add party labels and extraneous information to your parliament plot"
author: "Zoe Meers"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

source("../R/parliament_data.R")
source("../R/helper_funcs.R")
source("../R/draw_majoritythreshold.R")
source("../R/draw_legislaturelabels.R")
source("../R/theme_ggparliament.R")
library(dplyr)
library(magrittr)
library(ggplot2)


```

`ggparliament` has two functions for adding labels to parliament plots. The first (`draw_partylabels()`) plots the abbreviated name of parties and the total number of seats allocated to the party. The second (`draw_totalseats()`) plots the total number of parliamentarians in the center of the plot.
**Note:** Currently, these functions only work with the semicircle and horseshoe style parliament.

# Drawing party labels

```{r, fig.width=6, fig.height=4}
data <- ggparliament::election_data %>% 
    filter(year == "2016" & 
             country == "USA" & 
             house == "Representatives")

usa_data <- parliament_data(election_data = data, 
                            type = "semicircle", 
                            party_seats = data$seats, 
                            parl_rows = 8)

ggplot(usa_data, aes(x, y, color=party_long)) + 
    geom_parliament_seats() + 
    labs(colour = NULL) +
    draw_partylabels(party_names = TRUE,
                     party_seats = TRUE,
                     type = "semicircle") +
    scale_colour_manual(values = usa_data$colour, 
                        limits = usa_data$party_long) +
    theme_ggparliament(legend = FALSE) 
```

```{r,fig.width=4, fig.height=4}
australia <- election_data %>%
  filter(country == "Australia" &
    house == "Representatives" &
    year == 2016) 

australia_horseshoe <- parliament_data(election_data = australia,
  party_seats = australia$seats,
  parl_rows = 4,
  type = "horseshoe")

au <- ggplot(australia_horseshoe, aes(x, y, colour = party_short)) +
  geom_parliament_seats() + 
  theme_ggparliament(legend = FALSE) +
  labs(colour = NULL, 
       title = "Australian Parliament") +
  draw_partylabels(type = "horseshoe") + 
  scale_colour_manual(values = australia$colour, 
                      limits = australia$party_short) 

au
```



# Draw label noting total number of parliamentarians

```{r, fig.width=6, fig.height=4}
data <- ggparliament::election_data %>% 
    filter(year == "2016" & 
             country == "USA" & 
             house == "Representatives")

usa_data <- parliament_data(election_data = data, 
                            type = "semicircle", 
                            party_seats = data$seats, 
                            parl_rows = 8)

ggplot(usa_data, aes(x, y, color=party_long)) + 
    geom_parliament_seats() + 
    labs(colour = NULL) +
    draw_totalseats(n = 435,
                    type = "semicircle") +
    scale_colour_manual(values = usa_data$colour, 
                        limits = usa_data$party_long) +
    theme_ggparliament(legend = FALSE) 
```


