---
title: "How to highlight government or party in control of the legislature"
author: "Zoe Meers"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

source("../R/parliament_data.R")
source("../R/helper_funcs.R")
source("../R/draw_majorityline.R")
source("../R/draw_legislaturelabels.R")
library(tidyverse)
election_data <- readRDS(file="../data/election_data.rda")

```

## Highlighting governments or parties in control of legislative chamber


`election_data` has a dummy variable for government -- i.e. 1 for the party is part of the government, 0 otherwise.

This means we can specify whether a party is a part of the government (or otherwise has control of the legislature if they have a majority) in our visualization by using  `geom_highlight_government()`.

`geom_highlight_government()` surrounds the circle with a black outline. An example is as follows:

### 115th Congress

```{r}
us_congress <- election_data %>%
  filter(country == "USA" &
    year == 2016 &
    house == "Representatives")
head(us_congress)
```

```{r}
us_congress1 <- parliament_data(election_data = us_congress,
  type = "semicircle",
  total_seats = sum(us_congress$seats),
  parl_rows = 10,
  party_names = us_congress$party_short,
  party_seats = us_congress$seats)
head(us_congress1)
```

```{r, fig.width=6, fig.height=4}
ggplot(us_congress1, aes(x, 
                         y, 
                         colour = party_short)) +
  geom_parliament_seats() + 
  geom_highlight_government(government == 1) + #specify the variable you want to highlight here!
  theme_void() +
  labs(colour = NULL, 
       title = "United States Congress") +
  scale_colour_manual(values = us_congress1$colour, 
                      limits = us_congress1$party_short) 
```

**Note:** the United States Congress is currently controlled by the GOP but note that it can be be controlled by an opposing party if the opposing party has a majority in Congress. In the data for the US, the 'government' dummy variable shows the party that has control over the legislative chamber, not necessarily the government as a whole.

Additionally, this function is *not* limited to highlighting governments. If you want to highlight the front bench in Austrlia, for example, you can write
```{r}
australia <- election_data %>%
  filter(country == "Australia" &
    house == "Representatives" &
    year == 2016) 

australia1 <- parliament_data(election_data = australia,
  total_seats = sum(australia$seats),
  party_seats = australia$seats,
  parl_rows = 4,
  type = "horseshoe")
```

```{r,fig.width=4, fig.height=4}
au <- ggplot(australia1, aes(x, 
                            y, 
                            colour = party_short)) +
  geom_parliament_seats() + 
  geom_highlight_government(row == 1) + # this highlights the front bench.
  theme_void() +
  labs(colour = NULL, 
       title = "Australian Parliament") +
  scale_colour_manual(values = australia$colour, 
                      limits = australia$party_short) + 
  theme(legend.position = 'bottom') 
au
```
