---
title: "How to add party labels and extraneous information to your parliament plot"
author: "Zoe Meers"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
source("../R/parliament_data.R")
source("../R/helper_funcs.R")
source("../R/draw_majorityline.R")
source("../R/draw_legislaturelabels.R")
library(tidyverse)

```

`ggparliament` has two functions for adding labels to parliament plots. The first (`draw_partylabels()`) plots the abbreviated name of parties and the total number of seats allocated to the party. The second (`draw_totalseats()`) plots the total number of parliamentarians in the center of the plot.
**Note:** Currently, these functions only work with the semicircle and horseshoe style parliament.

# Drawing party labels

```{r, fig.width=6, fig.height=4}
data <- ggparliament::election_data %>% 
    filter(year == "2016" & 
               country == "USA" & 
               house == "Representatives")
usa_data <- parliament_data(election_data = data, 
                            type = "semicircle", 
                            party_seats = data$seats, 
                            party_names = data$party_short, 
                            parl_rows = 8, 
                            total_seats = sum(data$seats))
ggplot(usa_data, aes(x, 
                     y, 
                     color=party_long)) + 
    geom_parliament_seats() + 
    labs(colour = NULL) +
    draw_partylabels(type = 'semicircle', 
                     party_names = TRUE, 
                     party_seats = TRUE) +
    scale_colour_manual(values = usa_data$colour, 
                        limits = usa_data$party_long) +
    theme_void() + 
    theme(legend.position = "none") 
```

# Draw label noting total number of parliamentarians

```{r, fig.width=6, fig.height=4}
data <- ggparliament::election_data %>% 
    filter(year == "2016" & 
               country == "USA" & 
               house == "Representatives")
usa_data <- parliament_data(election_data = data, 
                            type = "semicircle", 
                            party_seats = data$seats, 
                            party_names = data$party_short, 
                            parl_rows = 8, 
                            total_seats = sum(data$seats))
ggplot(usa_data, aes(x, 
                     y, 
                     color=party_long)) + 
    geom_parliament_seats() + 
    labs(colour = NULL) +
    draw_totalseats(type = 'semicircle', 
                    n = 435) +
    scale_colour_manual(values = usa_data$colour, 
                        limits = usa_data$party_long) +
    theme_void() + 
    theme(legend.position = "none") 
```
